---
title: "p8105_hw6_yz4186"
author: "Yunxi Zhang"
date: "12/4/2021"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)
library(p8105.datasets)
library(modelr)
library(mgcv)
library(rvest)
knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```


## Problem 1

#### Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

```{r}
## check for missing data
anyNA(read_csv("./birthweight.csv"))

## convert numeric to factor
birthweight_df = 
  read_csv("./birthweight.csv") %>% 
 mutate(
    babysex = as.factor(babysex),
    frace = as.factor(frace),
    malform = as.factor(malform),
    mrace = as.factor(mrace)
  ) 
```


#### Load and clean the data for regression analysis (i.e. convert numeric to factor where appropriate, check for missing data, etc.).

#### Propose a regression model for birthweight. This model may be based on a hypothesized structure for the factors that underly birthweight, on a data-driven model-building process, or a combination of the two. Describe your modeling process and show a plot of model residuals against fitted values – use add_predictions and add_residuals in making this plot.

#### Compare your model to two others:

#### One using length at birth and gestational age as predictors (main effects only) One using head circumference, length, sex, and all interactions (including the three-way interaction) between these Make this comparison in terms of the cross-validated prediction error; use crossv_mc and functions in purrr as appropriate.

#### Note that although we expect your model to be reasonable, model building itself is not a main idea of the course and we don’t necessarily expect your model to be “optimal”.


construct the two models.

```{r}
lm_mod1 = lm(bwt ~ blength + gaweeks, data = birthweight_df)
broom::tidy(lm_mod1)

lm_mod2 = lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = birthweight_df)
broom::tidy(lm_mod2)
```

propose the regression model for birthweight using all predictors.
And then check AIC.

```{r }
mod_all = lm(bwt ~ .,data = birthweight_df)
broom::tidy(mod_all) 

step(mod_all, direction = 'backward') %>% broom::tidy() 
```

According to the result, we can find some reasonable predictors.

```{r }
mod_fit = lm(bwt ~ fincome + frace + parity + mrace + babysex + mheight+ ppwt+ gaweeks + smoken + wtgain + blength + bhead, data = birthweight_df)
broom::tidy(mod_fit)
```

make a plot.

```{r }
birthweight_df %>% 
  add_predictions(mod_fit) %>% 
  add_residuals(mod_fit) %>% 
  ggplot(aes( x = pred, y = resid)) +
  geom_point(alpha = 0.5)
```

From the plot I found that all the points are centered at 0 which makes sense. 
And most points are scatter around the prediction. However, some points are departure towards left in prediction and some are departure 


##### Model comparison

Cross validation.

```{r }
cv_df = crossv_mc(birthweight_df, 100)

cv_df = 
  cv_df %>% 
  mutate(
    mod1 = map(.x = train, ~lm(bwt ~ blength + gaweeks, data = birthweight_df)),
    mod2 = map(.x = train, ~lm(bwt ~ bhead + blength + babysex + bhead*blength + blength*babysex + bhead*babysex + bhead*blength*babysex, data = birthweight_df)),
    mod_fit = map(.x = train, ~lm(bwt ~ fincome + frace + parity + mrace + babysex + mheight+ ppwt+ gaweeks + smoken + wtgain + blength + bhead, data = birthweight_df))
  ) %>% 
  mutate(
    rmse_mod1 = map2_dbl(.x = mod1, .y = test, ~rmse(model = .x, data =.y)),
    rmse_mod2 = map2_dbl(.x = mod2, .y = test, ~rmse(model = .x, data =.y)),
    rmse_fit = map2_dbl(.x = mod_fit, .y = test, ~rmse(model = .x, data =.y))
  )
```

Compute RMSE.

```{r }
cv_df %>% 
  select(starts_with("rmse")) %>% 
  pivot_longer(
    everything(),
    names_to = "model",
    values_to = "rmse",
    names_prefix = "rmse_"
  ) %>% 
  ggplot(aes(x = model, y = rmse, color = model)) + geom_violin() +
  labs(
    x = "Model",
    y = "RMSE",
    title = "RMSEs of 3 models"
  )
```
From the plot, I found that the fitted model has the smallest RMSE which indicates that it is the best model among the three models.















